Approximation as Differentiation notes

### 2025-03-09 notes/sec/biproduct.tex
More general statement of prod/coprod lemma.
Reorient prod/coprod diagram.

\begin{proposition}
\label{prop:biproduct:prod-coprod}
Suppose $C$ a category with biproducts. Then the following diagram in $C$ commutes for any $f_1, g_1, f_2,
g_2$:

\begin{center}
\begin{tikzcd}[row sep=3em]
   & A' \\
   A \arrow[ur, "f_1"] \arrow[r, "\inj_A", shift left] &
   A \biprod B \arrow[l, "\proj_A", shift left] \arrow[r, "\proj_B"', shift right] \arrow[u, pos=0.3, "\coprodM{f_1}{g_1}"'] &
   B \arrow[l, "\inj_B"', shift right] \arrow[ul, "g_1"'] \\
   & B' \arrow[ul, "f_2"] \arrow[u, pos=0.6, "\prodM{f_2}{g_2}"'] \arrow[ur, "g_2"']
\end{tikzcd}
\end{center}
\end{proposition}

>>>>

\begin{proposition}
\label{prop:biproduct:prod-coprod}
Suppose $C$ a category with biproducts. Then the following commutes for any morphisms $f_1, g_1, f_2,
g_2$ in $C$:

\begin{center}
\begin{tikzcd}[row sep=3em, column sep=3em]
   & A \arrow[d, "\inj_A", shift left] \arrow[dr, "f_2"] \\
   A' \arrow[r, "\prodM{f_1}{g_1}"] \arrow[dr, "g_1"'] \arrow[ur, "f_1"] & A \biprod B \arrow[u, "\proj_A", shift left] \arrow[d, "\proj_B"', shift right] \arrow[r, pos=0.35, "\coprodM{f_2}{g_2}"] & B' \\
   & B \arrow[u, "\inj_B"', shift right] \arrow[ur, "g_2"']
\end{tikzcd}
\end{center}
\end{proposition}
